Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-16 Writing/appendix.rmd

>>>>

## Appendix E: CNN performance per training epoch
The below figure shows training and validation loss measured by mean square error (MSE) over the number of epochs in one of the thousand CNN simulation under aabbyytt scenario.

```{r, fig.width=4, fig.height=4, fig.cap = "An example of CNN performance per training epoch (scenario: aabbyytt)"}
knitr::include_graphics(here("GitControlled/Writing/loss_model4_simID1.png"))
```
